---
title: "R Notebook"
output: html_notebook
---
# Question 1
```{r}
library(tidyverse)
library(CodeClanData)
```

```{r}
backpack
```

# question 2
```{r}
backpack %>% 
  ggplot(aes(x=backpack_weight))+
  geom_density()
```
#Question 3
Are there differences in backpack weight between sex?
```{r}
backpack %>% 
  ggplot(aes(x=backpack_weight))+
  geom_density()+
  facet_grid(~sex)
```
```{r}
backpack %>% 
  ggplot(aes(x=backpack_weight))+
  geom_bar()+
  facet_grid(~sex)
```

#Question 4
What is the relationship between body weight and backpack weight?
```{r}
backpack %>% 
  ggplot(aes(x=backpack_weight, y=body_weight))+
  geom_point()+
  geom_smooth()
```
#question 5
What is the relationship between body weight and backpack weight? Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.
```{r}
backpack %>% 
  ggplot(aes(x=backpack_weight, y=body_weight))+
  geom_point()+
  geom_smooth()+
  facet_grid(~sex)
```
#question 6
What proportion of students report back pain?

```{r}
backpack %>% 
  mutate(back_pain = ifelse(back_problems > 0, TRUE, FALSE)) %>% 
  ggplot()+
  geom_bar(aes(x="", fill=back_pain))+
  coord_polar("y", start=0)
```
#question 7
What proportion of students report back pain? Is this proportion different between men and women?
```{r}
backpack %>% 
  mutate(back_pain = ifelse(back_problems > 0, TRUE, FALSE)) %>% 
  ggplot()+
  geom_bar(aes(x=sex, fill=back_pain), position="fill")
```

#question 8 
Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.

Try both backpack_weight and body_weight as well as the ratio.
```{r}
backpack %>% 
  mutate(back_pain = ifelse(back_problems > 0, TRUE, FALSE)) %>% 
  ggplot() +
  aes(x = backpack_weight,  y = body_weight, colour = back_pain, shape = sex) +
  geom_point(size = 4) +
  facet_grid(~sex)
```
