---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(infer)
data(msleep)
```

## Q2: Jabberwockies sleep for around 7 hours a night, on average. Perform an appropriate statistical test to determine whether the mean sleep_total in the sampled population of animal types differs from the typical value for jabberwockies.

a = 0.05
H0: mean sleep_total in the sample differ
Ha: mean sleep_total in the sample doesn't differ

# Jabberwocky is not on data, so we can sample the data without filtering.

```{r}
observed_stat_sleep <- msleep %>% 
  summarise(mean_sleep_total = mean(sleep_total))
observed_stat_sleep
```
# creating a hull dist

```{r}
null_distribution_sleep <- msleep %>% 
  specify(response = sleep_total) %>% 
  hypothesise(null = "point", mu = 7) %>% 
  generate(reps = 2000, type = "bootstrap") %>% 
  calculate(stat = "mean")
```
```{r}
null_distribution_sleep %>% 
  visualise(bins=25)
```

```{r}

null_distribution_sleep %>% 
  visualise(bins = 25)+
  shade_p_value(obs_stat = observed_stat_sleep$mean_sleep_total, direction = "both")
```
```{r}
null_distribution_sleep %>% 
  get_p_value(
    obs_stat = observed_stat_sleep$mean_sleep_total, 
    direction = "both"
  
  )
```

Answer: p=0. 
p value is less than or equal to α, so we reject the null hypothesis in favour of the alternative hypothesis.
Ha is right: average mean sleep total in the sampled population of animal types doesn't differ from the typical value for jabberwockies.

##Q3

Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average.


## Q4
Question 4. Perform an appropriate statistical test to determine whether the proportion of domesticated animal types in the population of animal types is greater than 5%.
H0: it is greater
Ha: it is not.
a = 0.05

```{r}
msleep_tidy <- msleep %>% 
  drop_na(conservation)
```
```{r}
observed_stat_animals <- msleep_tidy %>% 
  group_by(conservation) %>% 
  summarise(prop = n()/nrow(msleep_tidy)) %>% 
  filter(conservation == "domesticated")
```
```{r}
msleep_domesticated <- msleep_tidy %>% 
  mutate(domestication = ifelse(conservation == "domesticated", 
                                  "Yes", "No"))
null_distribution_dom <- msleep_domesticated %>% 
  specify(response = domestication, success = "Yes") %>% 
  hypothesise(null = "point", p = 0.015) %>% 
  generate(reps = 2000, type = "draw") %>% 
  calculate(stat = "prop") 
```
```{r}
null_distribution_dom %>% 
  visualise(bins = 15) +
  shade_p_value(obs_stat = observed_stat_animals$prop, direction="greater")
```
```{r}
null_distribution_dom %>% 
  get_p_value(obs_stat = observed_stat_animals$prop, direction="greater")
```
p is smaller than our treshold 0.05. We fail to reject the H0, and it means that the population of domesticated types is not greater than 5%.




