---
title: "Probability Consolidation Questions"
output: html_notebook
---
```{r setup}
library(tidyverse)
library(gtools)
source("prob.R")

```

Question 1.
If I roll a six-sided dice once, what is the probability of getting a number less than 5?

# p = n(event_outcomes)/ n(total_outcomes)
p = 4/6 = 2/3

Question 2.
How many outcomes are there in the sample space of an experiment in which we toss three dice?


```{r}
s_three_dice <- rolldie(3, nsides = 6)
s_three_dice
```

6*6*6 = 216

Question 3.
In an experiment where we roll four dice:
1) how many outcomes are in the event where the total of the four dice equals 5, 6, or 7?
2) what is the probability of this event?
3) what assumptions do we apply in answering part ii?
```{r}
s_four_dice_5 <- rolldie(4, nsides = 6) %>%  
  mutate(total = X1 + X2 + X3 + X4) %>% 
  filter(total==5)
nrow(s_four_dice_5)
```
Answer: 4 outcomes
```{r}
s_four_dice_6 <- rolldie(4, nsides = 6) %>%  
  mutate(total = X1 + X2 + X3 + X4) %>% 
  filter(total==6)
nrow(s_four_dice_6)
```
Answer: 10 outcomes
```{r}
s_four_dice_7 <- rolldie(4, nsides = 6) %>%  
  mutate(total = X1 + X2 + X3 + X4) %>% 
  filter(total==7)
nrow(s_four_dice_7)
```
Answer: 20 outcomes

```{r}
s_four_dice_567 <- rolldie(4, nsides = 6) %>%  
  mutate(total = X1 + X2 + X3 + X4) %>% 
  filter(total== 5 | total== 6 | total== 7)
nrow(s_four_dice_567)
```
answer: 34 outcomes

Question 3:
2) what is the probability of this event?

```{r}
s_four_dice_total <- rolldie(4, nsides = 6) 
p <- nrow(s_four_dice_567)/nrow(s_four_dice_total)
p
```
Answer: 34/1296 = 0.02623457


Question 4.
Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?
```{r}
people <- c(1,2,3,4,5)
chairs <- as_tibble(permutations(n=5, r=5, v=people, repeats.allowed = FALSE)) 
ordered_heights <- chairs %>% 
 filter(V1 ==5, V2 == 4, V3 == 3, V4 == 2, V5 == 1)

p= nrow(ordered_heights)/nrow(chairs)
p
```
Answer: 1/120 = 0.008333333

Question 5
I roll six dice:
1) what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?
2) what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?

```{r}
roll1 <- rolldie(6, nsides = 6)
roll2 <- roll1 %>% 
 filter(X1 == 6, X2 == 5, X3 == 4, X4 == 3, X5 == 2, X6 == 1)
p= nrow(roll2)/nrow(roll1)
p
```
Answer 1) probability of this event is only 1/46,656 = 0.00002143347

```{r}

dice <- c(1,2,3,4,5,6)
results <- as_tibble(permutations(n=6, r=6, v=dice, repeats.allowed = FALSE)) 
nrow(results)
```
Answer 2) 720
